shrimp_goby_boatnoise

### 2024-08-22 ms_boatnoise_shrimp_goby.Rmd
remove text
annotating code
error fishing

shrimp_species <- read.csv("./2-data/species.csv")

length(unique(BORIS_output$code))

#binding the decoder to the BORIS output and revealing the treatment and stage
BORIS_output$code <- str_sub(BORIS_output$video_id, 2,)
BORIS_output$code <- as.factor(BORIS_output$code)
shrimp_species$code <- as.factor(shrimp_species$code)
Video_codes$code <- as.factor(Video_codes$code)
decoded_dataframe <- inner_join(inner_join(BORIS_output, Video_codes, by = c("code")), shrimp_species, by = c("code"))
```

>>>>

#reading in shrimp species information
shrimp_species <- read.csv("./2-data/species.csv")
#error fishing
#binding the decoder to the BORIS output and revealing the treatment and stage
BORIS_output$code <- str_sub(BORIS_output$video_id, 2,)
BORIS_output$code <- as.factor(BORIS_output$code)
shrimp_species$code <- as.factor(shrimp_species$code)
Video_codes$code <- as.factor(Video_codes$code)
decoded_dataframe <- inner_join(inner_join(BORIS_output, Video_codes, by = c("code")), shrimp_species, by = c("code"))
```
